---
author: "Annie Griebie"
date: "`r Sys.Date()`"
output: 
  html_document:
    df_print: paged
---

# Reproducible Image and Online Resources
An image of this project as of *`r Sys.Date()* can be accessed by [clicking this link].
An interactive web app is available by [clicking this link instead] (https://anniepsy8960datascience.shinyapps.io/shiny_week8/).


# Script Settings and Resources
```{r,setup, message=FALSE}
setwd(dirname(rstudioapi::getActiveDocumentContext()$path))
library(tidyverse)
library(lubridate)
```

#Data Import and Cleaning 
I imported the week3 data set into the week8_tbl. I reverse scored Q5, I used the rowwise function to apply my subsequent commands to all the rows of  week8_tbl otherwise, then I used mutate to create new variables while preserving old variables, the new variables I wanted to create were two variables that contained participants mean scores of Q1-Q6, and also Q8-10. 
```{r, data_import_and_cleaning}
week8_tbl <- read_csv("../data/week3.csv") %>%
  mutate(q5 = recode(q5, "1"="5", "2"="4","3"="3", "4"="2", "5"="1")) %>% 
  mutate(q5=as.numeric(q5)) %>%
  rowwise() %>%
  mutate(meanQ1Q6 = mean(c(q1:q6)))%>%
  mutate(meanQ8Q10 = mean(c(q8:q10)))
```


## Visualization
I used the select function to display contained in Q1-Q6 because I already loaded tidyverse and the selection function is part of dplyr which is in tidyverse, it allows me to refer to just those variables. To make the display paginated I did (COMEBACK). I then used ggplot2 to display a scatterplot of participants mean scores on Q1-Q6 by their mean scores on Q8-Q10, using the geom_point function and retained the "se=T" command to display the shaded error band.
```{r, visualization, message=FALSE, echo=FALSE}
week8_tbl%>%
  select(q1:q6)

ggplot(week8_tbl, aes(x=meanQ1Q6, y=meanQ8Q10))+
  geom_point()+
  geom_smooth(method = "lm", se=T, color="purple")+
  labs(x="Mean scores on Q1-Q6", y="Mean scores on Q8-Q10")
```

## Analysis
I used the cor.test function to find the correlation between participants mean scores on Q1-Q6 and Q8-10. 
```{r, analysis}
cor.test(week8_tbl$meanQ1Q6, week8_tbl$meanQ8Q10)
```
I observed a correlation of `r `week8_tbl$meanQ1Q6, week8_tbl$meanQ8Q10`. The p-value is observed to be 0.5184 which is greater than an alpha value set to 0.05 or 0.01, thus suggesting the correlation is not statistically significant. 

## Data Export
I removed data columns that are not needed for the shiny app to make the datatable "skinny". I relabeled the gender column. 
```{r, data_export}
week8_tbl %>%
  select(-q7, -timeStart)%>%
  mutate(gender = factor(gender, levels = c("M", "F"), labels = c("Male",  "Female")))%>%
  mutate(timeEnd =ymd_hms(timeEnd)) %>%
  saveRDS(file = "../shiny_week8/shiny_data_week8.rds")
```
