---
author: "Annie Griebie"
date: "`r Sys.Date()`"
output: 
  html_document:
    df_print: paged
---

# Reproducible Image and Online Resources
An image of this project as of *`r Sys.Date()* can be accessed by [clicking this link].
An interactive web app is available by [clicking this link instead].


# Script Settings and Resources
```{r,setup, message=FALSE}
setwd(dirname(rstudioapi::getActiveDocumentContext()$path))
library(tidyverse)
```

#Data Import and Cleaning 
I imported the week3 data set into the week8_tbl. I reverse scored Q5, I used the rowwise function to apply my subsequent commands to all the rows of  week8_tbl otherwise, then I used mutate to create new variables while preserving old variables, the new variables I wanted to create were two variables that contained participants mean scores of Q1-Q6, and also Q8-10. 
```{r, data_import_and_cleaning}
week8_tbl <- read_csv("../data/week3.csv") %>%
  mutate(q5 = recode(q5, "1"="5", "2"="4","3"="3", "4"="2", "5"="1")) %>% 
  mutate(q5=as.numeric(q5)) %>%
  rowwise() %>%
  mutate(meanQ1Q6 = mean(c(q1:q6)))%>%
  mutate(meanQ8Q10 = mean(c(q8:q10)))
```
